Predictive Regressions with Persistent Regressors

### 2019-09-09 paper.tex
ADD power and rm .DS_Store

For the test-statistic to have a standard normal distribution under the null Campbell and Yogo (2006) propose to recenter and rescale which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as Campbell and Yogo call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression $r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}$. This regression can be interpreted as regressing the de-noised returns onto the regressor $x_{t-1}$ where we exploit the information contained in $\rho$ and the correlation of the shocks.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}!=0$, the t-statistic does not converge to a standard-normal distribution. Instead, as shown by Elliott and Stock (1994), under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\begin{equation}
\underline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma_{ue}}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}-1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
and 
\begin{equation}
\overline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}+1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
A 5\% one-sided or 10\% two-sided test of $H_0: \beta = 0$ is based on the 90\% Bonferroni confidence interval
$$[\underline{\beta}(\overline{\rho}), \overline{\beta}(\underline{\rho})]$$

@@

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rate close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates}
\centering
\label{tab:cy_changed}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

For the test-statistic to have a standard normal distribution under the null Campbell and Yogo (2006) propose to recenter and rescale which results in 
\begin{equation}
\frac{\sum_{t=1}^{T} x_{t-1}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{2}\right)^{1 / 2}}>C
\end{equation}
Revoking the previous assumption of $\alpha=\gamma=0$ and generalizing instead to any unknown  $\alpha$ and $\gamma$ by replacing $x_{t-1}$ by its demeaned value $x_{t-1}^{\mu}$, the test
\begin{equation}
Q\left(\beta_{0}, \rho\right)=\frac{\sum_{t=1}^{T} x_{t-1}^{\mu}\left[r_{t}-\beta_{0} x_{t-1}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)\right]}{\sigma_{u}\left(1-\delta^{2}\right)^{1 / 2}\left(\sum_{t=1}^{T} x_{t-1}^{\mu 2}\right)^{1 / 2}}>C
\end{equation}
is UMP conditional on $\sum_{t=1}^{T} x_{t-1}^{\mu 2}$.
This Q-statistic, as Campbell and Yogo call it, has an intuitive interpretations when $\beta_{0} = 0$. It is the t-statistic of the $\beta^{\star}$ coefficient in the regression
 \begin{equation}
 \label{eqn:r_star}
r_{t}-\beta_{u e}\left(x_{t}-\rho x_{t-1}\right)=\alpha^{\star}+\beta^{\star} x_{t-1}+v_{t}. 
\end{equation}
Regression ($\ref{eqn:r_star}$) can be interpreted as regressing the de-noised returns onto the regressor $x_{t-1}$, where the information contained in $\rho$ and the correlation of the shocks is exploited.
When $\beta_{u e}=0$, i.e., the correlation of the shocks is zero, the Q-statistic simplifies to the t-statistic which converges to a standard-normal distribution in this case. When $\beta_{u e}\neq0$, the t-statistic does not converge to a standard-normal distribution. Instead, as shown by Elliott and Stock (1994), under local-to-unity asymptotic theory it has the null distribution 
\begin{equation}
t\left(\beta_{0}\right) \Rightarrow \delta \frac{\tau_{c}}{\kappa_{c}}+\left(1-\delta^{2}\right)^{1 / 2} Z
\end{equation}
where $\left(W_{u}(s), W_{e}(s)\right)^{\prime}$ is a two-dimensional Wiener process with correlation $\delta$, $J_{c}(s)$ is defined by $\mathrm{d} J_{c}(s)=c J_{c}(s) \mathrm{d} s+\mathrm{d} W_{e}(s)$ with $J_{c}(0)=0$, $Z$ is a standard normal random variable independent of $\left(W_{e}(s), J_{c}(s)\right)$, $\kappa_{c}=\left(\int J_{c}^{\mu}(s)^{2} \mathrm{d} s\right)^{1 / 2}$, and $\tau_{c}=\int J_{c}^{\mu}(s) \mathrm{d} W_{e}(s)$.

@@

\begin{equation}
\underline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma_{ue}}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}-1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
and 
\begin{equation}
\overline{\beta}(\rho)=\widehat{\beta}(\rho)+\frac{T-2}{2} \frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{e} \widehat{\omega}}\left(\frac{\widehat{\omega}^{2}}{\widehat{\sigma}_{v}^{2}}-1\right) \operatorname{SE}(\widehat{\rho})^{2}+1.645\left(1-\widehat{\delta}^{2}\right)^{1 / 2} \operatorname{SE}(\widehat{\beta})
\end{equation}
A 5\% one-sided or 10\% two-sided test of $H_0: \beta = 0$ is based on the 90\% Bonferroni confidence interval
$$[\underline{\beta}(\overline{\rho}), \overline{\beta}(\underline{\rho})]$$
\subsection{Power comparison}
\label{power}
Campbell and Yogo (2006) evaluate the power of the feasible Q-test under local-to-unity asymptotics. In this framework the OLS estimators $\hat{\beta}$ and $\hat{\rho}$ are consistent at rate $T$. Thus, to have a meaningful comparison, local alternatives of the form $\beta = \beta_0 + b/T$ are considered where $b$ is a constant. The feasible Q-test is found to dominate the feasible t-test in all cases considered with increasing relative power gain in increasing $|\delta|$ and decreasing $|c|$. Their analysis shows that in the case of a highly persistent regressor, using the Q-test over the t-test provides a comparatively important gain in power. Their numerical refinement of the Bonferroni method provides a substantial further gain in power for the Q-test since this test exploits information about $\rho$. This makes its confidence interval for $\beta$ given $\rho$ more sensitive to $\rho$. Hence, without the refinement the Bonferroni Q-test is too conservative.

@@

Next, slightly different input parameters are chosen. If the results differ qualitatively, the previous findings might be the result of selection bias. As demonstrated by Table~\vref{tab:cy_changed}, no such suspicion is warranted. As long as the sample size is at least 100 and $\rho$ is local to unity, the Bonferroni Q-test has acceptable finite sample rejection rates. The infeasible Q-test, unsurprisingly, always has rejection rates close to $\alpha$. The t-test, on the other hand, significantly over-rejects when the innovations are highly correlated and $\rho$ is local to unity. It should be noted, however, that the two-sided Bonferroni Q-test tends to under-reject for the chosen parameters. 
\begin{table}[h!]
\caption{Finite-sample rejection rates}
\centering
\label{tab:cy_changed}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrr}
  \hline
 & Obs & $c$ & $\rho$ & $\delta$ & t-test & Bonf. Q-test & Q-test & Bonf. Q-test (two-sided) \\ 
  \hline
1 & 50 & 0 & 1.000 & -0.99 & 0.4442 & 0.0863 & 0.0544 & 0.0864 \\ 
  2 & 50 & 0 & 1.000 & -0.90 & 0.3786 & 0.0943 & 0.0506 & 0.0953 \\ 
  3 & 50 & -1 & 0.980 & -0.99 & 0.3502 & 0.0857 & 0.0486 & 0.0898 \\ 
  4 & 50 & -1 & 0.980 & -0.90 & 0.3107 & 0.0949 & 0.0489 & 0.0964 \\ 
  5 & 50 & -10 & 0.804 & -0.99 & 0.1440 & 0.0821 & 0.0512 & 0.1004 \\ 
  6 & 50 & -10 & 0.804 & -0.90 & 0.1226 & 0.0840 & 0.0472 & 0.0929 \\ 
  7 & 50 & -15 & 0.706 & -0.99 & 0.1114 & 0.0895 & 0.0485 & 0.1112 \\ 
  8 & 50 & -15 & 0.706 & -0.90 & 0.1035 & 0.0981 & 0.0468 & 0.1112 \\ 
  9 & 150 & 0 & 1.000 & -0.99 & 0.4467 & 0.0508 & 0.0508 & 0.0509 \\ 
  10 & 150 & 0 & 1.000 & -0.90 & 0.3804 & 0.0524 & 0.0494 & 0.0554 \\ 
  11 & 150 & -1 & 0.993 & -0.99 & 0.3584 & 0.0475 & 0.0493 & 0.0611 \\ 
  12 & 150 & -1 & 0.993 & -0.90 & 0.3137 & 0.0572 & 0.0532 & 0.0625 \\ 
  13 & 150 & -10 & 0.934 & -0.99 & 0.1510 & 0.0468 & 0.0480 & 0.0720 \\ 
  14 & 150 & -10 & 0.934 & -0.90 & 0.1309 & 0.0534 & 0.0484 & 0.0672 \\ 
  15 & 150 & -15 & 0.901 & -0.99 & 0.1273 & 0.0446 & 0.0520 & 0.0819 \\ 
  16 & 150 & -15 & 0.901 & -0.90 & 0.1133 & 0.0484 & 0.0489 & 0.0695 \\ 
  17 & 200 & 0 & 1.000 & -0.99 & 0.4477 & 0.0435 & 0.0478 & 0.0438 \\ 
  18 & 200 & 0 & 1.000 & -0.90 & 0.3786 & 0.0501 & 0.0520 & 0.0546 \\ 
  19 & 200 & -1 & 0.995 & -0.99 & 0.3582 & 0.0449 & 0.0483 & 0.0607 \\ 
  20 & 200 & -1 & 0.995 & -0.90 & 0.3127 & 0.0542 & 0.0468 & 0.0615 \\ 
  21 & 200 & -10 & 0.950 & -0.99 & 0.1490 & 0.0401 & 0.0497 & 0.0666 \\ 
  22 & 200 & -10 & 0.950 & -0.90 & 0.1352 & 0.0486 & 0.0502 & 0.0634 \\ 
  23 & 200 & -15 & 0.925 & -0.99 & 0.1276 & 0.0369 & 0.0487 & 0.0786 \\ 
  24 & 200 & -15 & 0.925 & -0.90 & 0.1234 & 0.0482 & 0.0491 & 0.0670 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed and two-tailed Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}
